### 2021-11-18 aifin/2021/project3/project3.tex
aifin project3

\lecture{Project 2: Paper Replication Study}{Yuan Yao}{Due: 23:59 Sunday 14 Nov, 2021}{21 Oct, 2021}

@@

This project as a warm-up aims to explore basic techniques in machine learning.
\begin{enumerate}
\item Pick up ONE (or more if you like) favourite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to {\bf FOUR} persons per group, to work on the same problem. Each team just submit {\bf ONE} report, \emph{with a clear remark on each person's contribution}. The report can be in the format of either a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
or \emph{technical report within 8 pages}, e.g. NIPS conference style (preferred format) 
\begin{center}
\url{https://nips.cc/Conferences/2019/PaperInformation/StyleFiles}, 
\end{center}
with source codes such as Python (Jupyter) Notebooks with a detailed documentation.
\item For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{mailto:aifin.hkust@gmail.com}{aifin.hkust@gmail.com}) with a title ``\underline{MATH6010z: Project 2}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\subsection{Replication studies}
In this reproduction process, we mainly focus on understanding the data preparation (how to transfer 1D time series data to 2D images representing historical market data), model design (CNN architecture design and mechanism behind it), workflow design (from training to model tuning and finally to prediction), performance evaluation and finally the interpretation part.

@@

    \begin{figure}
        \centering
        \includegraphics[width=.3\textwidth]{img/1.png}
        \hspace{0.5in}
        \includegraphics[width=.3\textwidth]{img/2.png}
        \caption{Examples of 20-day Image with volume bar and moving average line}
        \label{20-day image}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.25\textwidth, height=0.45\textwidth]{img/cnn.png}
        \caption{Diagram of CNN model}
        \label{cnn model}
    \end{figure}

@@

\section{Paper replication: Empirical Asset Pricing via Machine Learning}

@@

% \section{Kaggle Contest: Home Credit Default Risk}

% Many people struggle to get loans due to insufficient or non-existent credit histories. And, unfortunately, this population is often taken advantage of by untrustworthy lenders.

% Home Credit strives to broaden financial inclusion for the unbanked population by providing a positive and safe borrowing experience. In order to make sure this underserved population has a positive loan experience, Home Credit makes use of a variety of alternative data--including telco and transactional information--to predict their clients' repayment abilities.

% While Home Credit is currently using various statistical and machine learning methods to make these predictions, they're challenging Kagglers to help them unlock the full potential of their data. Doing so will ensure that clients capable of repayment are not rejected and that loans are given with a principal, maturity, and repayment calendar that will empower their clients to be successful.

% Visit the following website to join the competition.

% \url{https://www.kaggle.com/c/home-credit-default-risk/}

% {\bf Requirements}. For Kaggle contests, please register your team with name in the format of math6010z\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

@@

\section*{Peer Review}

In this exercise of open peer review, please write down your comments of the \emph{reports rather than of your own team} in the following format. Be considerate and careful with a precise description, avoiding offensive language.

{\bf Deadline is \emph{11:59pm November 19, 2021}}. Submit your review in plain text to the email address (\url{aifin.hkust@gmail.com}) with title: \underline{MAFS6010Z: Project 2 Review}. Rebuttal is open afterwards.

%Your review assignment can be found at

%{\centering{\url{https://deeplearning-math.github.io/2019/project1/project1review_assignment.pdf} }}

%\noindent where each student (SID) is randomly assigned with 5 group reports (excluding your own reports). You should submit reviews at least for these assignments, but more reviews are welcome with additional bonus credit.

%You should put each review in a plain text separately with a title  comprising the corresponding group number (\textbf{not your own group}) and your name (e.g., \emph{\underline{rev1\_group03\_Ian\_Goodfellow.pdf}}). Submit all your reviews in a single zip file \textbf{using canvas}. Rebuttal is open afterwards.

\begin{itemize}
\item Summary of the report.
\item Describe the strengths of the report. 
\item Describe the weaknesses of the report.
\item Evaluation on Clarity and quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
\item Evaluation on Technical Quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
\item Confidence on your assessment (1-3)
(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
\end{itemize}
%
%%Then please vote your top THREE favourite reports on Doodle: 
%%\url{xxx}
%
\newpage

\section*{Rebuttal}
The rebuttal period starts from now, till \emph{11:59pm Nov 22, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.

The following tips of rebuttal might be helpful for you to follow:

1. The main aim of the rebuttal is to answer any specific questions that the reviewers might have raised, or to clarify any misunderstanding of the technical content of the paper.

2. Keep your rebuttal short, to-the-point, and specific. In our experience, such rebuttals have the maximum impact.

3. Always be polite and professional. Refrain from name calling or rude comments, especially in response to negative reviews.

4. Highlight the changes in your manuscripts had you made a simple revision.

>>>>

\lecture{Project 3: Final}{Yuan Yao}{Due: 23:59 Sunday 12 Dec, 2021}{18 Nov, 2021}

@@

This project as a warm-up aims to explore basic techniques in machine learning.
\begin{enumerate}
\item Pick up ONE (or more if you like) favourite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to {\bf FOUR} persons per group, to work on the same problem. Each team just submit 
\subitem(a) \emph{ONE report}, \emph{with a clear remark on each person's contribution}. The report can be in the format of either a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
or \emph{technical report within 8 pages}, e.g. NIPS conference style (preferred format) 
\begin{center}
\url{https://nips.cc/Conferences/2019/PaperInformation/StyleFiles}, 
\end{center}
with source codes such as Python (Jupyter) Notebooks with a detailed documentation.

\subitem(b) \emph{ONE short presentation video within 10 mins}, e.g. in Youtube or Bilibili link. You may submit your presentation slides together with the video link to help understanding.

\item For Kaggle contests, please register your team with name in the format of math6010z\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{mailto:aifin.hkust@gmail.com}{aifin.hkust@gmail.com}) with a title ``\underline{MATH6010z: Project 3}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\subsubsection{Replication studies}
In this reproduction process, we mainly focus on understanding the data preparation (how to transfer 1D time series data to 2D images representing historical market data), model design (CNN architecture design and mechanism behind it), workflow design (from training to model tuning and finally to prediction), performance evaluation and finally the interpretation part.

@@

    \begin{figure}
        \centering
        \includegraphics[width=.3\textwidth]{../project2/img/1.png}
        \hspace{0.5in}
        \includegraphics[width=.3\textwidth]{../project2/img/2.png}
        \caption{Examples of 20-day Image with volume bar and moving average line}
        \label{20-day image}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.25\textwidth, height=0.45\textwidth]{../project2/img/cnn.png}
        \caption{Diagram of CNN model}
        \label{cnn model}
    \end{figure}

@@

\subsection{Empirical Asset Pricing via Machine Learning}

@@

\section{Kaggle Contest in Project 1: Home Credit Default Risk}

Many people struggle to get loans due to insufficient or non-existent credit histories. And, unfortunately, this population is often taken advantage of by untrustworthy lenders.

Home Credit strives to broaden financial inclusion for the unbanked population by providing a positive and safe borrowing experience. In order to make sure this underserved population has a positive loan experience, Home Credit makes use of a variety of alternative data--including telco and transactional information--to predict their clients' repayment abilities.

While Home Credit is currently using various statistical and machine learning methods to make these predictions, they're challenging Kagglers to help them unlock the full potential of their data. Doing so will ensure that clients capable of repayment are not rejected and that loans are given with a principal, maturity, and repayment calendar that will empower their clients to be successful.

Visit the following website to join the competition.

\url{https://www.kaggle.com/c/home-credit-default-risk/}

%{\bf Requirements}. For Kaggle contests, please register your team with name in the format of math6010z\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

@@

%\newpage
%
%\section*{Peer Review}
%
%In this exercise of open peer review, please write down your comments of the \emph{reports rather than of your own team} in the following format. Be considerate and careful with a precise description, avoiding offensive language. 
%
%{\bf Deadline is \emph{11:59pm November 19, 2021}}. Submit your review in plain text to the email address (\url{aifin.hkust@gmail.com}) with title: \underline{MAFS6010Z: Project 2 Review}. Rebuttal is open afterwards.
%
%%Your review assignment can be found at
%
%%{\centering{\url{https://deeplearning-math.github.io/2019/project1/project1review_assignment.pdf} }}
%
%%\noindent where each student (SID) is randomly assigned with 5 group reports (excluding your own reports). You should submit reviews at least for these assignments, but more reviews are welcome with additional bonus credit. 
%
%%You should put each review in a plain text separately with a title  comprising the corresponding group number (\textbf{not your own group}) and your name (e.g., \emph{\underline{rev1\_group03\_Ian\_Goodfellow.pdf}}). Submit all your reviews in a single zip file \textbf{using canvas}. Rebuttal is open afterwards.
%
%\begin{itemize}
%\item Summary of the report.
%\item Describe the strengths of the report. 
%\item Describe the weaknesses of the report.
%\item Evaluation on Clarity and quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
%\item Evaluation on Technical Quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
%\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
%\item Confidence on your assessment (1-3)
%(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
%\end{itemize}
%%
%%%Then please vote your top THREE favourite reports on Doodle: 
%%%\url{xxx}
%%
%\newpage
%
%\section*{Rebuttal}
%The rebuttal period starts from now, till \emph{11:59pm Nov 22, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.
%
%The following tips of rebuttal might be helpful for you to follow:
%
%1. The main aim of the rebuttal is to answer any specific questions that the reviewers might have raised, or to clarify any misunderstanding of the technical content of the paper.
%
%2. Keep your rebuttal short, to-the-point, and specific. In our experience, such rebuttals have the maximum impact.
%
%3. Always be polite and professional. Refrain from name calling or rude comments, especially in response to negative reviews.
%
%4. Highlight the changes in your manuscripts had you made a simple revision.
%
%%
